% ============================================================
% Omni-Scanner Semantic v2.1
% Enterprise Security Briefing -- Bilingual EN / ES
% Audience: C-Suite, Banking & Financial Regulators,
%           National Security Agencies
%
% Compile: pdflatex (twice)
% ============================================================

\documentclass[11pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english, spanish]{babel}
\usepackage[a4paper, top=2.8cm, bottom=2.8cm, left=3.2cm, right=3.2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{float}
\usepackage{tcolorbox}
\tcbuselibrary{breakable, skins}
\usepackage[
  colorlinks=true,
  linkcolor=duranteamber,
  urlcolor=duranteblue,
  pdftitle={Omni-Scanner Semantic v2.1 -- Enterprise Security Briefing},
  pdfauthor={Gonzalo Emir Durante}
]{hyperref}

% Colors
\definecolor{duranteamber}{RGB}{180,130,0}
\definecolor{duranteblue}{RGB}{24,75,145}
\definecolor{darkgray}{RGB}{40,40,40}
\definecolor{lightgray}{RGB}{248,248,246}
\definecolor{alertred}{RGB}{160,30,30}
\definecolor{solidgreen}{RGB}{20,90,45}
\definecolor{codebg}{RGB}{24,24,24}
\definecolor{codetext}{RGB}{210,210,190}

% Boxes
\newtcolorbox{statbox}{
  colback=lightgray, colframe=duranteamber,
  fontupper=\small, boxrule=0.6pt, arc=2pt, breakable}

\newtcolorbox{alertbox}[1][]{
  colback=alertred!6, colframe=alertred!70,
  fonttitle=\bfseries\small, coltitle=white,
  attach boxed title to top left={yshift=-2mm, xshift=4mm},
  boxed title style={colback=alertred!80, arc=1pt},
  title=#1, breakable}

\newtcolorbox{solidbox}[1][]{
  colback=solidgreen!5, colframe=solidgreen!60,
  fonttitle=\bfseries\small,
  attach boxed title to top left={yshift=-2mm, xshift=4mm},
  boxed title style={colback=solidgreen!70, coltext=white, arc=1pt},
  title=#1, breakable}

\newtcolorbox{hashbox}{
  colback=codebg, colframe=duranteamber!50,
  fontupper=\ttfamily\footnotesize\color{codetext}, breakable}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\footnotesize\color{duranteamber}\textbf{OMNI-SCANNER SEMANTIC v2.1}}
\fancyhead[R]{\footnotesize\color{darkgray} RESTRICTED --- ENTERPRISE BRIEFING}
\fancyfoot[C]{\footnotesize\color{darkgray}\thepage}
\fancyfoot[R]{\footnotesize\color{darkgray}
  \textcopyright{} 2026 G.E. Durante --- Durante Invariance License v1.0}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{%
  \hbox to\headwidth{\color{duranteamber}\leaders\hrule height 0.4pt\hfill}}

% Sections
\titleformat{\section}{\large\bfseries\color{darkgray}}{\thesection}{1em}{}
  [\color{duranteamber}\hrule\vspace{2pt}]
\titleformat{\subsection}{\normalsize\bfseries\color{darkgray}}{\thesubsection}{1em}{}

\title{%
  {\Large\bfseries\color{darkgray} OMNI-SCANNER SEMANTIC v2.1}\\[6pt]
  {\large\color{duranteamber}
    Topological Integrity Auditing for Artificial Intelligence Systems}\\[4pt]
  {\normalsize\color{darkgray}
    Enterprise Security Briefing --- Restricted Distribution}
}
\author{%
  \textbf{Gonzalo Emir Durante}\\
  \small Architect --- Durante Semantic Stability Framework\\
  \small \href{https://zenodo.org/records/19052627}{DOI: 10.5281/zenodo.19052627}
  \quad Registry: EX-2026-18792778 (TAD, Argentina)\\
  \small \href{https://github.com/Leesintheblindmonk1999/Omni_Scanner}%
    {github.com/Leesintheblindmonk1999/Omni\_Scanner}
}
\date{March 2026 --- v2.1}

% =====================================================================
\begin{document}
% =====================================================================

\maketitle
\thispagestyle{fancy}

\begin{center}
\fbox{\parbox{0.6\textwidth}{\centering\small
  \textbf{Language / Idioma:}\quad
  \hyperlink{sec:en}{\textbf{English}} \quad|\quad
  \hyperlink{sec:es}{\textbf{Español}}\\[2pt]
  \textit{Both sections contain the complete briefing.}
}}
\end{center}
\vspace{4pt}

\begin{statbox}
\centering
\textbf{Classification:} Restricted \quad
\textbf{Version:} 2.1 \quad
\textbf{Date:} March 2026\\
\textbf{Prior Art:} OTS Bitcoin anchor --- March 10, 2026 \quad
\textbf{Registry:} EX-2026-18792778 (TAD Argentina)
\end{statbox}

\newpage

% =====================================================================
% ENGLISH
% =====================================================================
\hypertarget{sec:en}{}
\selectlanguage{english}

\section*{\color{darkgray}Executive Summary}

\begin{statbox}
Financial institutions, regulatory bodies, and critical infrastructure operators
increasingly delegate analytical and decisional functions to large-scale AI
systems. These systems operate as statistical engines: they do not reason ---
they generate outputs that are statistically plausible given their training
distribution. \textbf{When that distribution diverges from operational reality,
the output remains fluent, confident, and wrong.}

The Omni-Scanner Semantic v2.1 is a forensic-grade auditing instrument that
detects structural inconsistencies in AI-generated outputs through topological
data analysis --- without access to model weights, training data, or internal
architecture. It operates on the output alone.

The system is fully sovereign: it runs locally, requires no external API calls,
and produces cryptographically signed audit reports suitable for legal and
regulatory proceedings.
\end{statbox}

\section{The Structural Integrity Gap in Deployed AI Systems}

\subsection{What Current Safety Filters Do Not Detect}

Contemporary AI safety mechanisms --- content filters, alignment layers, output
moderation --- operate at the \emph{lexical} level. They detect prohibited
keywords and known harmful patterns. They do not inspect the \emph{geometric
structure} of the reasoning embedded in the output.

A language model can produce text that is syntactically correct, stylistically
fluent, free of any flagged content, and simultaneously internally contradictory
at the logical structure level. This condition --- what the technical literature
terms \emph{hallucination} --- is undetectable by any lexical filter or human
reviewer operating at production speed.

\begin{alertbox}[Documented Operational Risk Categories]
\begin{tabularx}{\linewidth}{lX}
\toprule
\textbf{Domain} & \textbf{Failure Mode} \\
\midrule
Banking \& Credit & AI risk assessments with structurally inconsistent logical
  chains --- conclusions not supported by the stated evidence \\
Legal \& Compliance & Contract review that misses coercive clauses introduced
  through paraphrasing that preserves surface plausibility \\
Regulatory Reporting & Summaries that selectively compress or invert the
  logical structure of source documents \\
Procurement & AI-assisted drafting that introduces asymmetric obligations
  through strategic vagueness \\
\bottomrule
\end{tabularx}
\end{alertbox}

These failures share a common property: they are \textbf{invisible to surface-level
review} because the output is fluent. The structural problem is geometric,
not lexical. A different class of instrument is required to detect it.

\section{Omni-Scanner Semantic v2.1 --- Technical Architecture}

\subsection{Operating Principle: Geometry Over Lexicon}

The Omni-Scanner treats a document or AI-generated output as a geometric object
embedded in a high-dimensional semantic space. Rather than asking
\emph{``what does this text say?''}, it asks
\emph{``what is the topological structure of the reasoning manifold?''}

Inconsistencies invisible at the word level --- contradictions introduced through
paraphrasing, logical loops, strategic vagueness --- manifest as measurable
deformations in this manifold. The system detects them through three independent
structural metrics combined into the \textbf{ManifoldScore}:

\begin{table}[H]
\centering
\caption{ManifoldScore component metrics and detection targets.}
\begin{tabular}{p{3.8cm} p{5.2cm} p{4.6cm}}
\toprule
\textbf{Metric} & \textbf{What it measures} & \textbf{Primary detection} \\
\midrule
Shannon Entropy & Information density of the token distribution &
  Strategic vagueness, repetition \\
Higuchi Fractal Dimension & Roughness of the word-length time series &
  Synthetic regularity (LLM artifacts) \\
TF-IDF k-NN Coherence & Topological connectivity of sentence embeddings &
  Logical fragmentation, circular arguments \\
\bottomrule
\end{tabular}
\end{table}

\subsection{The Durante Constant --- $\kappa_D = 0.56$}

The ManifoldScore is evaluated against a single operational threshold derived
through five independent mathematical convergences \cite{durante2026manifold}:
Statistical Thermodynamics, Percolation Theory, Rate-Distortion Theory,
Lyapunov Stability, and the Golden Ratio. The convergence value is
$\kappa_D = 0.56$.

\begin{statbox}
\centering
$M \geq 0.56$ \;:\; Structural integrity within operational bounds\\[4pt]
$M < 0.56$ \;:\; Manifold structurally compromised --- escalate for review
\end{statbox}

This threshold is not a heuristic. It is a derived operational constant with
cryptographically established temporal priority, registered March 10, 2026,
anchored in the Bitcoin blockchain via OpenTimestamps.

\subsection{Topological Semantic Diff --- Structural Manipulation Detection}

Given two versions of a document --- original and AI-processed, or two model
outputs on the same input --- the system computes the Wasserstein $p{=}2$
distance between their H\textsubscript{1} persistence diagrams. The result
is the \textbf{Invariant Similarity Index} (ISI):

\[
\mathrm{ISI}(A,B) = \max\!\left(0,\min\!\left(1,
  1 - \frac{W_2(A,B)}{2\,\kappa_D}\right)\right)
\]

If $\mathrm{ISI} < \kappa_D$, a \textbf{Structural Manipulation Alert} is
triggered. This detection is \textbf{language-agnostic}: a structurally
manipulated English contract and a structurally manipulated Spanish contract
produce the same topological signature. The geometry of manipulation is
invariant to the lexicon.

\begin{table}[H]
\centering
\caption{Semantic Diff verdict thresholds.}
\begin{tabular}{lll}
\toprule
\textbf{Verdict} & \textbf{Condition} & \textbf{Operational Meaning} \\
\midrule
\texttt{IDENTICAL} & $W_2 \approx 0$ & No structural change \\
\texttt{MINOR\_DRIFT} & $W_2 < 0.056$ & Within-threshold variation \\
\texttt{STRUCTURAL\_CHANGE} & $W_2 \in [0.056, 0.56]$ & Significant, sub-alert \\
\texttt{MANIFOLD\_RUPTURE} & $\mathrm{ISI} < 0.56$ &
  \textbf{Structural Manipulation Alert} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Live Stream Monitor --- Invariance Shield}

For real-time AI monitoring, the Live Stream Monitor applies sliding-window
ManifoldScore analysis to continuous output. When the score drops below
$\kappa_D$ for $N$ consecutive windows, the system triggers an
\textbf{Incoherence Disconnection} --- a mathematical safety valve that halts
the stream and flags the output for review.

This is structurally different from content moderation. It does not require
a prohibited-content library. It detects incoherence from the geometry of
the output, regardless of subject matter or language.

\begin{table}[H]
\centering
\caption{Invariance Shield state machine.}
\begin{tabular}{lll}
\toprule
\textbf{State} & \textbf{Condition} & \textbf{Action} \\
\midrule
\texttt{OK} & All windows $\geq \kappa_D$ & Continue \\
\texttt{WARNING} & Score $< \kappa_D$, below $N_{\max}$ & Flag for review \\
\texttt{DISCONNECT} & $N_{\max}$ consecutive drops & Halt, escalate \\
\bottomrule
\end{tabular}
\end{table}

\section{Sovereign Deployment Architecture}

\subsection{Zero External Dependencies at Audit Time}

\begin{itemize}[leftmargin=*]
  \item No API calls to OpenAI, Google, Anthropic, or any third-party service
  \item Full local execution on standard institutional hardware
  \item No access to model weights or training data required
  \item Bilingual detection corpus (English + Spanish) with no cloud lookup
\end{itemize}

An institution auditing outputs from a foreign AI provider does so without
transmitting any institutional content to that provider's infrastructure.
The audit is conducted entirely within the institution's security perimeter.

\subsection{Registered Intellectual Property}

\begin{solidbox}[Temporal Priority --- Cryptographically Established]
\begin{tabularx}{\linewidth}{lX}
\toprule
\textbf{Record} & \textbf{Details} \\
\midrule
Administrative registry & EX-2026-18792778 --- TAD, Jefatura de Gabinete de
  Ministros, Rep\'{u}blica Argentina \\
Blockchain anchor & OpenTimestamps on Bitcoin blockchain, March 10, 2026.
  Three independent OTS records (v1.1, v2.0 EN, v2.0 ES) \\
Scientific record & Zenodo DOI 10.5281/zenodo.19052627 --- open access,
  CERN infrastructure, citable in legal proceedings \\
License & Durante Invariance License v1.0 --- commercial deployment requires
  attribution and explicit license \\
\bottomrule
\end{tabularx}
\end{solidbox}

\section{Forensic-Grade Audit Trail}

\subsection{Immutable Verdict Signing}

Each audit verdict is sealed with a deterministic SHA-256 hash:
\[
h = \mathrm{SHA256}\!\left(
  \mathrm{JSON}_{\mathrm{sorted}}\!\left\{
    h_{\text{doc}},\; \kappa_D,\; M,\; t,\; v,\; \texttt{"omni-v2.1"}
  \right\}
\right)
\]

The same inputs always produce the same hash. Any party with access to the
original document can independently verify the audit record. Any post-generation
alteration of the ISI score or verdict invalidates the integrity checksum,
providing tamper evidence suitable for legal proceedings.

\subsection{NIST-Compatible Audit Report Structure}

The \texttt{--audit-report} flag generates a signed JSON report including:
author identification, license registry, timestamp UTC, random seed for
reproducibility, SHA-256 of the input document, ISI score with 95\% bootstrap
confidence interval, segment-level fracture localization, topological fingerprint
for deduplication, and integrity checksum.

\begin{hashbox}
\{\\
\quad "author": "Gonzalo Emir Durante",\\
\quad "license\_id": "Durante-Invariance-1.0-EX-2026-18792778",\\
\quad "isi\_score": 0.46481234,\\
\quad "verdict": "MANIFOLD\_RUPTURE",\\
\quad "bootstrap": \{"ci\_lower": 0.4521, "ci\_upper": 0.4775, "stable": true\},\\
\quad "integrity\_checksum": "a7f3c2d1e8b94f..."\\
\}
\end{hashbox}

\section{Proof of Concept --- Engagement Protocol}

A structured Proof of Concept engagement proceeds in four phases:

\begin{enumerate}[leftmargin=*, label=\textbf{Phase \arabic*.}]
  \item \textbf{Baseline Audit.} The institution provides a corpus of
    AI-generated outputs from its deployed systems (anonymized as required).
    The Omni-Scanner produces ManifoldScore and ISI distributions, establishing
    a structural integrity baseline.
  \item \textbf{Comparative Analysis.} Selected document pairs --- original
    vs AI-processed --- are submitted to the Semantic Diff engine. Structural
    divergences are localized to specific segments with XAI explanations.
  \item \textbf{Live Monitor Integration.} For institutions with active AI
    pipelines, the Invariance Shield is configured on a sample of real-time
    output. Shield events are logged and reviewed with the institution's team.
  \item \textbf{Forensic Report Delivery.} All findings are delivered as
    signed audit reports with integrity checksums, independently verifiable
    by the institution's own technical staff.
\end{enumerate}

\textbf{What the PoC does not require:} access to model weights or training
data, modification of existing AI infrastructure, transmission of institutional
data to external servers, or proprietary information leaving the institution's
environment.

\begin{statbox}
\textbf{To initiate a Proof of Concept engagement:}\\[4pt]
GitHub: \href{https://github.com/Leesintheblindmonk1999/Omni_Scanner}%
  {github.com/Leesintheblindmonk1999/Omni\_Scanner}\\
Scientific record: \href{https://zenodo.org/records/19052627}%
  {zenodo.org/records/19052627}\\
LinkedIn: \href{https://www.linkedin.com/in/gonzalo-emir-durante-8178b6277}%
  {linkedin.com/in/gonzalo-emir-durante-8178b6277}\\
Registry: EX-2026-18792778 --- TAD, Rep\'{u}blica Argentina
\end{statbox}

% =====================================================================
% SPANISH
% =====================================================================
\newpage
\hypertarget{sec:es}{}
\selectlanguage{spanish}

\begin{center}
{\Large\bfseries\color{darkgray} OMNI-SCANNER SEMÁNTICO v2.1}\\[6pt]
{\large\color{duranteamber}
  Auditoría Topológica de Integridad para Sistemas de Inteligencia Artificial}\\[4pt]
{\normalsize\color{darkgray}
  Briefing de Seguridad Corporativa --- Distribución Restringida}\\[8pt]
\fbox{\parbox{0.55\textwidth}{\centering\small
  \textbf{Navegación:}\quad
  \hyperlink{sec:en}{\textbf{English}} \quad|\quad
  \hyperlink{sec:es}{\textbf{Español}}
}}
\end{center}
\vspace{4pt}

\begin{statbox}
\centering
\textbf{Clasificación:} Restringido \quad
\textbf{Versión:} 2.1 \quad
\textbf{Fecha:} Marzo 2026\\
\textbf{Prior Art:} Anclado en Bitcoin --- 10 de Marzo de 2026 \quad
\textbf{Expediente:} EX-2026-18792778 (TAD Argentina)
\end{statbox}

\subsection*{Resumen Ejecutivo}

\begin{statbox}
Las instituciones financieras, organismos reguladores e infraestructuras críticas
delegan progresivamente funciones analíticas y decisionales en sistemas de IA de
gran escala. Estos sistemas operan como motores estadísticos: no razonan ---
generan outputs estadísticamente plausibles dada su distribución de entrenamiento.
\textbf{Cuando esa distribución diverge de la realidad operacional, el output
permanece fluido, seguro de sí mismo, y erróneo.}

El Omni-Scanner Semántico v2.1 es un instrumento de auditoría forense que detecta
inconsistencias estructurales en outputs de IA mediante análisis de datos topológicos
--- sin acceso a pesos del modelo, datos de entrenamiento ni arquitectura interna.
Opera sobre el output únicamente.

El sistema es completamente soberano: ejecuta localmente, no requiere llamadas a
APIs externas, y produce reportes de auditoría firmados criptográficamente, aptos
para procedimientos legales y regulatorios.
\end{statbox}

\subsection*{S.1\quad La Brecha de Integridad Estructural}

Los mecanismos de seguridad actuales de IA operan a nivel \emph{léxico}. Detectan
palabras prohibidas y patrones dañinos conocidos. No inspeccionan la
\emph{estructura geométrica} del razonamiento embebido en el output.

Un modelo de lenguaje puede producir texto sintácticamente correcto, estilísticamente
fluido, libre de cualquier contenido marcado, e internamente contradictorio a nivel
de estructura lógica. Esta condición --- denominada \emph{alucinación} en la literatura
técnica --- es indetectable por cualquier filtro léxico o revisor humano a velocidad
operacional.

\begin{alertbox}[Categorías de Riesgo Operacional Documentadas]
\begin{tabularx}{\linewidth}{lX}
\toprule
\textbf{Dominio} & \textbf{Modo de falla} \\
\midrule
Banca y Crédito & Evaluaciones de riesgo con cadenas lógicas estructuralmente
  inconsistentes --- conclusiones no respaldadas por la evidencia declarada \\
Legal y Compliance & Revisión de contratos que omite cláusulas coercitivas
  introducidas mediante parafraseo que preserva plausibilidad superficial \\
Reportes Regulatorios & Resúmenes que comprimen o invierten selectivamente la
  estructura lógica de los documentos fuente \\
Adquisiciones & Redacción asistida por IA que introduce obligaciones asimétricas
  mediante vaguedad estratégica \\
\bottomrule
\end{tabularx}
\end{alertbox}

Estas fallas comparten una propiedad: son \textbf{invisibles a la revisión
superficial} porque el output es fluido. El problema estructural es geométrico,
no léxico. Se requiere un instrumento de distinta clase para detectarlo.

\subsection*{S.2\quad Arquitectura Técnica del Omni-Scanner v2.1}

El Omni-Scanner trata un documento o output de IA como un objeto geométrico
embebido en un espacio semántico de alta dimensión. En lugar de preguntar
\emph{``¿qué dice este texto?''}, pregunta
\emph{``¿cuál es la estructura topológica del manifold de razonamiento?''}

Las inconsistencias invisibles a nivel léxico se manifiestan como deformaciones
medibles en este manifold. El sistema las detecta mediante tres métricas
estructurales independientes combinadas en el \textbf{ManifoldScore}:

\begin{table}[H]
\centering
\caption{Métricas del ManifoldScore y objetivos de detección.}
\begin{tabular}{p{3.8cm} p{5.2cm} p{4.6cm}}
\toprule
\textbf{Métrica} & \textbf{Qué mide} & \textbf{Detección principal} \\
\midrule
Entropía de Shannon & Densidad informacional de la distribución de tokens &
  Vaguedad estratégica, repetición \\
Dimensión Fractal de Higuchi & Rugosidad de la serie de longitudes de palabras &
  Regularidad sintética (artefactos LLM) \\
Coherencia TF-IDF k-NN & Conectividad topológica de embeddings de oraciones &
  Fragmentación lógica, argumentos circulares \\
\bottomrule
\end{tabular}
\end{table}

\textbf{La Constante de Durante $\kappa_D = 0.56$} es el umbral operacional
derivado mediante cinco convergencias matemáticas independientes \cite{durante2026manifold}:
Termodinámica Estadística, Teoría de Percolación, Teoría Rate-Distortion,
Estabilidad de Lyapunov, y la Razón Áurea.

\begin{statbox}
\centering
$M \geq 0.56$\;: Integridad estructural dentro de límites operacionales\\[4pt]
$M < 0.56$\;: Manifold estructuralmente comprometido --- escalar para revisión
\end{statbox}

\textbf{El Diff Semántico Topológico} compara dos versiones de un documento
mediante la distancia de Wasserstein entre sus diagramas de persistencia
H\textsubscript{1}. El \textbf{Índice de Similitud Invariante} (ISI) es
agnóstico al idioma: un contrato abusivo en inglés y uno en español producen
la misma firma topológica. La geometría de la manipulación es invariante al léxico.

\textbf{El Monitor de Stream en Vivo} aplica análisis por ventana deslizante a
outputs continuos. Cuando el score cae por debajo de $\kappa_D$ durante $N$
ventanas consecutivas, activa la \textbf{Desconexión por Incoherencia} ---
válvula de seguridad matemática que detiene el stream y escala la alerta. No
requiere biblioteca de contenido prohibido; detecta incoherencia desde la
geometría del output.

\subsection*{S.3\quad Arquitectura de Despliegue Soberano}

\begin{itemize}[leftmargin=*]
  \item Sin llamadas a APIs de OpenAI, Google, Anthropic ni terceros
  \item Ejecución local completa en hardware institucional estándar
  \item Sin acceso a pesos del modelo ni datos de entrenamiento
  \item Corpus de detección bilingüe (inglés + español) sin consultas externas
\end{itemize}

Una institución que audita outputs de un proveedor de IA extranjero lo hace sin
transmitir ningún contenido a la infraestructura de ese proveedor. La auditoría
se realiza íntegramente dentro del perímetro de seguridad de la institución.

\begin{solidbox}[Prioridad Temporal --- Establecida Criptográficamente]
\begin{tabularx}{\linewidth}{lX}
\toprule
\textbf{Registro} & \textbf{Detalles} \\
\midrule
Expediente administrativo & EX-2026-18792778 --- TAD, Jefatura de Gabinete de
  Ministros, República Argentina \\
Anclaje blockchain & OpenTimestamps en blockchain Bitcoin, 10 de Marzo de 2026.
  Tres registros OTS independientes (v1.1, v2.0 EN, v2.0 ES) \\
Registro científico & Zenodo DOI 10.5281/zenodo.19052627 --- acceso abierto,
  infraestructura CERN, citable en procedimientos legales \\
Licencia & Durante Invariance License v1.0 --- el despliegue comercial requiere
  atribución y licencia explícita del autor \\
\bottomrule
\end{tabularx}
\end{solidbox}

\subsection*{S.4\quad Registro Forense Inmutable}

Cada veredicto se sella con un hash SHA-256 determinístico. Los mismos inputs
siempre producen el mismo hash. Cualquier alteración posterior del puntaje ISI
o el veredicto invalida el checksum de integridad --- evidencia de manipulación
apta para procedimientos legales.

\subsection*{S.5\quad Protocolo de Prueba de Concepto}

\begin{enumerate}[leftmargin=*, label=\textbf{Fase \arabic*.}]
  \item \textbf{Auditoría de Línea de Base.} La institución provee un corpus de
    outputs de IA de sus sistemas desplegados (anonimizados según corresponda).
    El Omni-Scanner produce distribuciones de ManifoldScore e ISI.
  \item \textbf{Análisis Comparativo.} Pares de documentos seleccionados se
    someten al motor de Diff Semántico. Las divergencias estructurales se
    localizan en segmentos específicos con explicaciones XAI.
  \item \textbf{Integración del Monitor en Vivo.} El Escudo de Invarianza se
    configura sobre una muestra de output en tiempo real. Los eventos del
    Escudo se registran y revisan con el equipo de la institución.
  \item \textbf{Entrega del Reporte Forense.} Reportes firmados con checksums
    de integridad, verificables independientemente por el equipo técnico
    de la institución.
\end{enumerate}

\textbf{Lo que la PoC no requiere:} acceso a pesos del modelo, modificación
de infraestructura, transmisión de datos institucionales a servidores externos,
ni información propietaria fuera del entorno de la institución.

\begin{statbox}
\textbf{Para iniciar una Prueba de Concepto:}\\[4pt]
GitHub: \href{https://github.com/Leesintheblindmonk1999/Omni_Scanner}%
  {github.com/Leesintheblindmonk1999/Omni\_Scanner}\\
Registro científico: \href{https://zenodo.org/records/19052627}%
  {zenodo.org/records/19052627}\\
LinkedIn: \href{https://www.linkedin.com/in/gonzalo-emir-durante-8178b6277}%
  {linkedin.com/in/gonzalo-emir-durante-8178b6277}\\
Expediente: EX-2026-18792778 --- TAD, República Argentina
\end{statbox}

% =====================================================================
% BIBLIOGRAPHY
% =====================================================================
\selectlanguage{english}
\newpage
\begin{thebibliography}{9}

\bibitem{durante2026manifold}
Durante, G.E. (2026).
\textit{Project Manifold 0.56: Semantic Thermodynamic Invariance and the
Durante Constant ($\kappa_D = 0.56$) as a Universal AGI Stability Threshold.}
Zenodo, v43.0.
\href{https://zenodo.org/records/18901544}{zenodo.org/records/18901544}.
Registry: EX-2026-18792778.

\bibitem{durante2026scanner}
Durante, G.E. (2026).
\textit{Omni-Scanner Semantic: Topological Auditing and Forensic Invariance
for Large Language Models.}
Zenodo: \href{https://zenodo.org/records/19052627}{10.5281/zenodo.19052627}.

\bibitem{cohen2007}
Cohen-Steiner, D., Edelsbrunner, H., \& Harer, J. (2007).
\textit{Stability of persistence diagrams.}
Discrete \& Computational Geometry, 37(1), 103--120.

\bibitem{nist2023}
National Institute of Standards and Technology. (2023).
\textit{AI Risk Management Framework (AI RMF 1.0).} NIST AI 100-1.

\end{thebibliography}

\vspace{1cm}
\begin{center}
\small\color{duranteamber}
\textcopyright{} 2026 Gonzalo Emir Durante. All rights reserved.\\
Registry: EX-2026-18792778 $\cdot$ Zenodo $\cdot$ Durante Invariance License v1.0\\[4pt]
\textit{``Energy transforms, truth is conserved. 0.56 is the law.''}
\end{center}

\end{document}
